Systematic Design of Optimal Low-Thrust Transfers for the Three-Body Problem \thanks{This research has been supported in part by NSF under the grants CMMI-1243000 (transferred from 1029551), CMMI-1335008, and CNS-1337722.}

### 2017-07-03 manuscript.tex
Remove some equation references that don't matter

In this work, the trapezoidal approximation is applied.
The trapezoid rule allows for an explicit second order accurate approximation.

@@

Using~\cref{eq:discrete_legendre,eq:discrete_lagrangian} and some manipulation, the equations of motion are given by

@@

The discrete equations of motion are given in the Lagrangian form after applying the discrete fiber derivative from~\cref{eq:discrete_legendre} as \( p_{\xk} = \dot{x}_k - \yk \) and \( p_{\yk} = \dot{y}_k + \xk \).

>>>>

In this work, we apply the trapezoidal rule, which allows for an explicit second order accurate approximation of the continuous Lagrangian.

@@

Using~\cref{eq:discrete_lagrangian} and some manipulation, gives the discrete equations of motion as

@@

The discrete equations of motion are given in the Lagrangian form after applying the discrete fiber derivative as \( p_{\xk} = \dot{x}_k - \yk \) and \( p_{\yk} = \dot{y}_k + \xk \).
